Formalisation of Session-based Lambda Calculus Type Systems

### 2014-11-14 proposal/proposal.tex
Tweaking the pi-calculus section.

\citeauthor{Caires:2010:STI} \cite{Caires:2010:STI} present a connection between $\pi$-calculus type system with session types and intuitionistic linear logic. They equate linear propositions with session types of the process calculus via a bidirectional translation relation. They use a labelled transition system to represent process reduction with observable actions on channels. They represent dual intuitionistic linear logic as a sequent calculus providing logical connectives which have session-based interpretations. Process reduction steps are equated with proof reduction via cut elimination. The relationship with intuitionistic linear logic provides absence of deadlocks in session-based communication for the process calculus.

>>>>

\citeauthor{Caires:2010:STI} \cite{Caires:2010:STI} present a connection between $\pi$-calculus type system with session types and intuitionistic linear logic. They equate linear propositions with session types of the process calculus via a bidirectional translation relation. They use a labelled transition system to represent process reduction with observable actions on channels. They represent dual intuitionistic linear logic as a sequent calculus providing logical connectives which have session-based interpretations. Process reduction steps are equated with proof reduction via cut elimination. The relationship with intuitionistic linear logic provides absence of deadlocks in session-based communication for the process calculus. The correspondence of session types to linear logic propositions is an important step in providing a solid logical foundation for a concurrent type theory; in the same way ``sequential'' type theory ($\lambda$-calculi) profitted from a logical perspective. However, for session types to become a more usable tool for programming distributed communication systems (the ultimate goal, of course, is to write more correct programs), we cannot be expected to program directly in the $\pi$-calculus; a more mainstream programming paradigm must be built upon these solid logical foundations. With that in mind, enter the $\lambda$-calculus!
